---
title: "Binomial Model Updating"
author: "Justin Mann"
date: "2023-09-23"
output: html_document
runtime: shiny
---

```{r libraries, echo=FALSE}
library(tidyverse)
library(rethinking)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  numericInput("n_W", label = "Water tosses", 0, min = 0, max = 25),
  
  numericInput("n_L", label = "Land tosses", 0, min = 0, max = 25)
)

renderPlot({
W <- input$n_W
L <- input$n_L
curve(dbeta(x, W+1, L+1), from = 0, to = 1, xlab = "Proportion of water", ylab = "Density")
})
```



```{r binomial model plots}
# define grid
p_grid <- seq(from=0, to=1, length.out=20)

#define prior
prior <- rep(1,20)
prior <- ifelse(p_grid < 0.5, 0, 1)
prior <- exp(-5*abs(p_grid - 0.5))

# compute likelihood at each value in grid
likelihood <- dbinom(6, size = 9, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior, so it sums to 1
posterior <- unstd.posterior/sum(unstd.posterior)

plot(p_grid, posterior, type="b", 
     xlab="probability of water", ylab="posterior probability")
mtext("20 points")

```


```{r stat rethinking R code 2.6}
globe.qa <- quap(
  alist(
    W ~ dbinom(W+L, p), # binomial likelihood
    p ~ dunif(0,1) # uniform prior
  ),
  data = list(W=6,L=3)
)
precis(globe.qa)
```


```{r stat rethinking R code 2.7}
# analytical calculation 
W <- 3
L <- 0

curve(dbeta(x, W+1, L+1), from = 0, to = 1, xlab = "Proportion of water", ylab = "Density")

```


