---
title: "Binomial Model Updating"
author: "Justin Mann"
date: "2023-09-23"
output: html_document
runtime: shiny
---


```{r libraries, include=FALSE}
library(tidyverse)
library(rethinking)
```

```{r setup, include=FALSE}
# install.packages(c("coda","mvtnorm","devtools","loo","dagitty","shape"))
# devtools::install_github("rmcelreath/rethinking")
# devtools::install_github("stan-dev/cmdstanr")
```


## Anthrops vs. Disconnectors

At the end of our Socratic debate, you voted on whether 1) anthropomorphism or 2) disconnection from our evolutionary roots was the more troublesome source of bias when studying animal communication.

In this portion of our "Building the World in Models" lesson, I'd like you to think about how animals decide when they've collected enough information to make a sufficiently informed choice regarding their communication with other individuals. In other words, when do animals decide that they've collected enough data (SMALL WORLD) to accurately represent the realized outcome of their decisions (LARGE WORLD). 

In the exercise below, I've written some R code (with a little help from ChatGPT) that allows you to generate SMALL WORLD data from the LARGE WORLD true distribution of votes from our Anthrops vs. Disconnectors poll. This code essentially works like the marble example from the first part of this lesson. By clicking the "Generate Random Numbers" button, you are drawing three random votes out of the pool of your 24 total votes. Each time you click that button, you are again pulling three more votes out of the same pool of 24 total votes (like placing the marbles back in the bag after each sample).    



```{r random numbers 1, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 1"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```
```{r random numbers 2, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 2"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```
```{r random numbers 3, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 3"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```
```{r random numbers 4, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 4"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```
```{r random numbers 5, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 5"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```
```{r random numbers 6, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 6"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```
```{r random numbers 7, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 7"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```
```{r random numbers 8, echo=FALSE}
# Define the UI for the app
ui <- fluidPage(
  titlePanel("Random Number Generator 8"),
  sidebarLayout(
    sidebarPanel(
      actionButton("generate_button", "Generate Random Numbers")
    ),
    mainPanel(
      verbatimTextOutput("random_numbers")
    )
  )
)

# Define the server for the app
server <- function(input, output) {
  # Function to generate random numbers
  generateRandomNumbers <- function() {
    random_numbers <- sample(c(0, 1), 3, replace = TRUE, prob = c(12/24, 12/24))
    return(random_numbers)
  }
  
  # Event handler for the button click
  observeEvent(input$generate_button, {
    numbers <- generateRandomNumbers()
    output$random_numbers <- renderPrint({
      numbers
    })
  })
}

# Run the app
shinyApp(ui = ui, server = server)
```

```{r decision plot, echo=FALSE}
inputPanel(
  numericInput("n_W", label = "Anthropomorphism (1)", 0, min = 0, max = 50),
  
  numericInput("n_L", label = "Disconnection (0)", 0, min = 0, max = 50)
)

renderPlot({
W <- input$n_W
L <- input$n_L
curve(dbeta(x, W+1, L+1), from = 0, to = 1, xlab = "Proportion of votes (A/D)", ylab = "Density")
})
```





